%------------------------
% Harvey Walton - CV (ATS friendly, single page)
%------------------------

\documentclass[a4paper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header/footer
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.4in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{0.8in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedright

% Section formatting
\titleformat{\section}{\scshape\large}{}{0em}{}[\titlerule]

% Custom commands
\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\textbf{#1} \hfill #2 \\
  \textit{#3} \hfill \textit{#4}
}

\newcommand{\resumeItem}[1]{\item{#1}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,itemsep=0pt,parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Harvey Walton}} & \href{mailto:harveywalton.hw@gmail.com}{harveywalton.hw@gmail.com} \\
  \href{https://linkedin.com/in/harvey-walton}{linkedin.com/in/harvey-walton} & 07854275328 \\
  \href{https://github.com/hwalton}{github.com/hwalton} & Oxford \\
\end{tabular*}

\vspace{6pt}
\textbf{Mechanical Engineering | Probabilistic Machine Learning | Python | Go}

%----------EDUCATION-----------
\section{Education}

\resumeSubheading{University of Sheffield}{2019 -- 2024}{MEng Mechanical Engineering with a Year in Industry, 1st Class (Hons)}{Sheffield, UK}
\resumeItemListStart
  \resumeItem{Dissertation: A Python Machine Learning project using a probabilistic Gaussian Process model to improve robustness to noise in Fourier analysis of dynamic mechanical systems. (Supervisor: Tim Rogers).}
  \resumeItem{Awarded 2020-21 Mechanical Engineers' Prize for best examination performance in the department by a second-year undergraduate.}
  \resumeItem{Relevant Modules: Mathematics for Engineering Modelling (97\%), Control Engineering (94\%), Advanced Dynamics (86\%), Computational and Numerical Methods (80\%).}
\resumeItemListEnd

\resumeSubheading{A-Levels \& GCSEs}{2014 -- 2019}{}{Oxford, UK}

\vspace{-2em}

\resumeItemListStart
  \resumeItem{A-Levels: Mathematics (A*), Further Mathematics (A), Physics (A*).}
  \resumeItem{GCSEs: Mathematics (9), English Language (6), Physics (A*) and 8 Others.}
\resumeItemListEnd

%----------EXPERIENCE-----------------
\section{Experience}

\resumeSubheading{Assistant Design Engineer}{Sept 2022 -- June 2023}{HP Consulting Services Ltd}{Jet Engine Balancing Tools}
\resumeItemListStart
    \resumeItem{Led projects designing and manufacturing lifting tools supplied to Rolls-Royce.}
    \resumeItem{Certified designs for UKCA and CE compliance against industry standards as part of quality assurance responsibilities.}
    \resumeItem{Produced CAD models and detailed engineering drawings using SolidWorks and Siemens NX.}
    \resumeItem{Verified designs under load cases through Finite Element Analysis (FEA).}
    \resumeItem{Inspected dimensional and geometric tolerances (GD\&T) to ensure compliance with engineering drawings.}
\resumeItemListEnd

\resumeSubheading{Maths Tutor}{Aug 2024 -- Present}{Oxford International Study Centre \& Freelance}{Oxford, Remote}
\resumeItemListStart
\resumeItem{Deployed a Go/HTMX web app to provide flashcards to my students (see \href{https://github.com/hwalton/flashcard-app-showcase}{github.com/hwalton}).}
\resumeItem{Programmed scripts to automate testing and deployment, speeding up workflows and development cycles.}
\resumeItem{Developed a ``Process First'' approach to business operations through documentation of day-to-day activities in versioned standard operating procedures to ensure reliable, repeatable delivery.}
\resumeItem{Presented complex concepts to a non-technical audience on a daily basis.}
\resumeItem{Managed client relationships to ensure delivery satisfied requirements.}
\resumeItemListEnd


%----------PROJECTS-----------------
\section{Personal Projects}
\hfill\textit{Available at \href{https://github.com/hwalton}{github.com/hwalton}}

\textbf{Quant GP}
\resumeItemListStart
  \resumeItem{Built a probabilistic forecasting model for stochastic financial data (Python, Scikit-Learn).}
  \resumeItem{Designed an objective function to optimise portfolios under uncertainty for a subjective preference curve of outcomes.}
\resumeItemListEnd

\textbf{Gradient Boosted Regression}
\resumeItemListStart
  \resumeItem{Deployed a Scikit-Learn gradient boosted regressor model (California Housing dataset) with a full MLOps workflow to AWS EKS.}
  \resumeItem{Integrated MLflow, Airflow, Docker, Helm, and Kubernetes for orchestration and deployment.}
\resumeItemListEnd

\textbf{Xero Invoice Generator}
\resumeItemListStart
  \resumeItem{Created a Golang app integrating with Xero API to automate purchase order generation.}
  \resumeItem{Implemented SQL migrations, authentication flows, and CI/CD via GitHub Actions.}
\resumeItemListEnd

%----------REFERENCES-----------------
\section{References}
Available on request.

\end{document}